Assessing the Global COVID19 Impact on Air Transport with Open Data

### 2021-06-16 paper.Rmd
minors

1.2.1 Gather and prepare data
```{r}
#Reading and saving data
source("./R/list_apt_files.R")
file_names <- list_apt_files()
open_sky <- map_dfr(file_names, read_csv)
#write_csv(open_sky, "./data/open_sky.csv")

# Take a look
glimpse(open_sky)
str(open_sky)
summary(open_sky)

@@

#Visualizing something...
df1 <- fb2 %>% group_by(DATE = date(firstseen)) %>% summarize(count = n())
df1 %>% ggplot(aes(x = as.factor(year(DATE)))) +
  geom_boxplot(aes(y = count))

>>>>

1.2.1 Gather and prepare data
```{r}
#Reading and saving data
source("./R/list_apt_files.R")
file_names <- list_apt_files()
open_sky <- map_dfr(file_names, read_csv)
#write_csv(open_sky, "./data/open_sky.csv")
```

```{r}
# Take a look
glimpse(open_sky)
str(open_sky)
summary(open_sky)

@@

#Visualizing something...
df1 <- fb2 %>% group_by(DATE = date(firstseen)) %>% summarize(count = n())
df1 %>% ggplot(aes(x = as.factor(year(DATE)))) +
  geom_boxplot(aes(y = count))
# This is the daily traffic of Aprils, distributed as a boxplot, FOR THE WHOLE WORLD! Needs to filter.

#Filtering Brazilian and European data to reduce the sample (and csv) size
#Preparing airports file

bra_10_apts <- c("SBBR", "SBGR", "SBSP", "SBKP", "SBRJ", "SBGL", "SBCF", "SBSV", "SBPA", "SBCT")
eur_apts <- c("EHAM","LFPG","EGLL","EDDF","EDDM","LEMD","LIRF","LEBL","EGKK","LSZH")
study_airports <- c(bra_10_apts, eur_apts)
study_airports

fb2 <- fb2 %>% filter(origin %in% bra_10_apts | destination %in% bra_10_apts) %>% mutate(REG = "BRA", .before = typecode)
fb2
summary(fb2)

#airports <- read_csv("data-raw/airports.csv")
#airports <- airports %>% transmute(ICAO = ident, CONTINENT = continent, COUNTRY = iso_country, REGION = iso_region, NAME #= name, CITY = municipality) 
#airports <- airports %>% mutate(CONTINENT = case_when(is.na(CONTINENT) ~ "NA", TRUE ~ CONTINENT))
#airports
#write_csv(airports, "./data/airports_info.csv")
